\documentclass[english,10pt,letterpaper]{moderncv}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\usepackage{lastpage}
\geometry{verbose,tmargin=2cm,bmargin=1.5cm,lmargin=2cm,rmargin=2cm}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\usepackage{babel}
\usepackage{subscript}
\ifx\hypersetup\undefined
  \AtBeginDocument{%
    \hypersetup{unicode=true}
  }
\else
  \hypersetup{unicode=true}
\fi

\makeatletter

\moderncvstyle{classic}
\moderncvcolor{blue}
\firstname{Steve}
\familyname{Meisburger}
\title{Curriculum vitae}
\address{Cornell University}{Department of Chemistry \& Chemical Biology}{Baker Laboratory, Mail Box 224 \makenewline 259 East Ave. Ithaca, NY 14853}
\phone{(607) 255-4064}
\mobile{(xxx) xxx-xxxx} 
\email{spm82@cornell.edu}
\homepage{spmeisburger.github.io}
\setlength{\hintscolumnwidth}{1.8cm}

\lfoot{\addressfont\textcolor{gray}{Curriculum vitae: Steve Meisburger, Cornell (\today)}}
\rfoot{\addressfont\textcolor{gray}{Page \thepage\ of \pageref{LastPage}}}

\makeatother

\begin{document}


\makecvtitle{}{}

\section{Education}

\cventry{Aug. 2014}{Doctor of Philosophy}{Applied Physics, Cornell University}{Ithaca, NY}{}{}

\cvitem{}{Thesis: \emph{Ion interactions with single- and double-stranded DNA measured using solution X-ray scattering}.}
\cvitem{}{Advisor: Lois Pollack}

\cventry{May 2007}{Bachelor of Arts}{Physics, Carleton College}{Northfield, MN}{\emph{Summa cum laude}}{}

\section{Appointments}

\cventry{2020--}{Research Associate}{Chemistry \& Chemical Biology, Cornell University}{}{}{}
\cvitem{}{Advisor: Nozomi Ando}

\cventry{2018-2020}{Postdoctoral Research Associate}{Chemistry \& Chemical Biology, Cornell University}{}{}{}
\cvitem{}{Advisor: Nozomi Ando}

\cventry{2016-2018}{Postdoctoral Research Fellow}{Chemistry, Princeton University}{}{}{}
\cvitem{}{Support: NIH NRSA Postdoctoral Fellowship (F32)}
\cvitem{}{Advisor: Nozomi Ando}

\cventry{2014-2016}{Postdoctoral Research Associate}{Chemistry, Princeton University}{}{}{}
\cvitem{}{Advisor: Nozomi Ando}

\section{Awards and Honors}

\cventry{2016-2018}{NIH NRSA Postdoctoral Fellowship: ``Allosteric motions of B\textsubscript{12}
enzymes''}{Princeton University}{}{\href{https://grantome.com/grant/NIH/F32-GM117757-02}{F32-GM117757}. Sponsors: Nozomi Ando \& Garnet Chan (Princeton Chemistry)}{}

\cventry{May 2017}{Best Poster: Technical Achievement}{CHESS Users' Meeting}{}{}{}

\cventry{May 2017}{Travel Award}{American Crystallographic Association}{}{Meeting in New Orleans, LA}{}

\cventry{Apr. 2017}{Travel and Professional Development Award}{American Society for Biochemistry and Molecular Biology}{}{Meeting in Chicago, IL}{}

\cventry{2008-2011}{NIH Predoctoral Training Grant in Molecular Biophysics}{Cornell University}{}{\href{https://grantome.com/grant/NIH/T32-GM008267-26}{T32-GM008267}}{}

\cventry{May 2007}{Distinction awarded for Senior Integrative Exercise (Thesis)}{Carleton College}{}{}{}

\section{Teaching Experience}

\cventry{Apr. 2021}{Instructor}{High Pressure Biology Workshop}{Cornell High Energy Synchrotron Source}{(Remote)}{}

\cventry{(recurring)}{Instructor}{Everything BioSAXS: Getting started in biological small-angle x-ray solution scattering}{BioCAT beamline at Advanced Photon Source}{(Remote)}{Workshops in October 2020, March 2021}

\cventry{Aug. 2020}{Instructor}{Applications of Small Angle Scattering to Structural Biology: An Introduction}{Workshop at the ACA Annual Meeting}{(Remote)}{}

\cventry{(recurring)}{Instructor}{BioSAXS Essentials: Getting Started in Biological Small-Angle X-ray Solution Scattering}{Cornell High Energy Synchrotron Source}{Ithaca, NY}{Workshops in Nov. 2014, May 2016, May 2017, and April 2018}

\cventry{Oct. 2018}{Lecturer}{9th annual SIBYLS BioSAXS workshop}{Advanced Light Source}{Berkeley, CA}{}

\cventry{Fall 2018}{Guest Lecturer}{CHEM 2870: Introductory Physical Chemistry}{Cornell CCB}{}{}

\cventry{Fall 2015}{Guest Lecturer}{CHM 515: Biophysical Chemistry I}{Princeton Chemistry}{}{}

\cventry{Spring 2014}{Guest Lecturer}{CHM 516: Biophysical Chemistry II}{Princeton Chemistry}{}{}

\cventry{2007-2008}{Teaching Assistant}{AEP 3630: Electronic Circuits}{Cornell Applied \& Eng. Physics}{}{}

\section{Research Experience}

\cventry{2020--}{Researcher Associate}{Cornell Chemistry \& Chemical Biology}{}{}{Lab of Nozomi Ando}

\cventry{}{New methods for dynamic structural biology}{}{}{}{Developing algorithms and experimental methods for diffuse X-ray scattering, SAXS, and cryo-EM to reveal protein motions important for function.}

\cventry{2014-2020}{Postdoctoral Researcher}{Princeton Chemistry, Cornell Chemistry \& Chemical Biology}{}{}{Advisor: Nozomi Ando}

\cventry{}{Protein dynamics from diffuse X-ray scattering}{}{}{}{Developed experimental and computational methods to utilize the diffuse scattering between the Bragg peaks for measuring correlated protein motions within the crystal. Collaborators: David Case (Rutgers), Sol Gruner (Cornell), Eddie Arnold (Rutgers).}

\cventry{}{Allosteric motions of B\textsubscript{12} enzymes}{}{}{}{Investigated domain motions involved in regulating catalytic cycle of B\textsubscript{12}-dependent enzymes Methionine Synthase and Corrinoid FeS Protein / Methyltransferase using solution scattering and non-conventional X-ray crystallography.  Collaborator: Stephen Ragsdale (U. Michigan).}

\cventry{}{Allosteric regulation of phenylalanine hydroxylase}{}{}{}{Revealed role of domain motion in allosteric regulation by combining chromatography-coupled SAXS with mathematical deconvolution. Collaborator: Paul Fitzpatrick (UT Health San Antonio).}

\cventry{2008-2014}{Graduate Research Assistant}{Cornell Applied \& Engineering Physics}{}{}{Advisor: Lois Pollack}

\cventry{}{Instrumentation and methods for time-resolved SAXS and cryo-SAXS}{}{}{}{Designed and fabricated a microfluidic mixer and adapted a commercial stopped-flow mixer for time-resolved SAXS experiments on RNA folding and nucleosome disassembly. Developed methods for cryo-cooling compatible with SAXS data collection. Collaborators: Ken Hampel (U. Vermont Medical Center), Rob Thorne (Cornell).}

\cventry{}{Characterizing the unfolded state of nucleic acids and proteins}{}{}{}{
Investigated electrostatic effects on single-stranded RNA and DNA homopolymers using SAXS. Applied polymer theory and atomistic modeling to reconcile SAXS and single-molecule FRET data from nucleic acids and protein L in the unfolded state. Collaborators: Gilad Haran (Weizmann Institute), Kevin Plaxco (UCSB), Tobin Sosnick (U. Chicago).}

\cventry{}{Measuring and modeling the ion atmosphere around RNA and DNA}{}{}{}{Measured spatial distribution and number of positive ions surrounding DNA duplexes and RNA motifs using anomalous scattering from heavy atoms. Compared results with continuum electrostatic theory and atomistic simulations. Collaborators: Kurt Andresen (Gettysburg College), David Case (Rutgers), Ron Elber (U.T. Austin).}

\cventry{2006}{Undergraduate Researcher}{REU at the Santa Fe Institute}{Santa Fe, New Mexico}{}{Mentor: Alfred Hubler. Project: \emph{Chaos in Wall Following Robots.}}

\cventry{2005}{Undergraduate Researcher}{NNIN REU at Stanford University}{Palo Alto, California}{}{Mentors: Fabian Pease, Dan Pickard. Project: \emph{Characterization of Beam Aberrations due to Magnetic Field Tilt in DIVA for Massively Parallel Electron Beam Lithography.}}


\section{Publications}

%\cvitem{{[}27{]}}{\textbf{Meisburger SP}, Case DA, Ando N.
%\emph{Observing how ligand binding alters protein breathing motions with total X-ray scattering.} Manuscript in preparation.}

\cvitem{{[}26{]}}{\textbf{Meisburger SP}, Ando N.
\emph{Separating internal and external correlated protein motions in the crystalline state by total X-ray scattering analysis and vibrational dynamics simulation.} Submission scheduled for Feb. 2022.}

\cvitem{{[}25{]}}{Xu D{*}, \textbf{Meisburger SP}{*}, Ando N.
\emph{Correlated motions in structural biology.} \textbf{Biochemistry} 60: 2331-40 (2021). {*}equal contribution}

\cvitem{{[}24{]}}{\textbf{Meisburger SP}{*}, Xu D{*}, Ando N.
\emph{REGALS: a general method to deconvolve X-ray scattering data from evolving mixtures.} \textbf{IUCrJ} 8: 225-237 (2021). {*}equal contribution}

\cvitem{{[}23{]}}{\textbf{Meisburger SP}, Case DA, Ando N.
\emph{Diffuse X-ray Scattering from Correlated Motions in a Protein Crystal.} \textbf{Nat. Commun.} 11: 1271 (2020). }

\cvitem{{[}22{]}}{Khan CA, \textbf{Meisburger SP}, Ando N, Fitzpatrick PF.
\emph{The phenylketonuria-associated substitution R68S converts phenylalanine hydroxylase to a constitutively active enzyme but reduces its stability.} \textbf{J. Biol. Chem.} 294(12): 4359-67 (2019).}

\cvitem{{[}21{]}}{Parker MJ, Maggiolo AO, Thomas WC, Kim A, \textbf{Meisburger SP},
Ando N, Boal AK, Stubbe J. \emph{An endogenous dAMP ligand in Bacillus
subtilis class Ib RNR promotes assembly of a noncanonical dimer for
regulation by dATP.} \textbf{PNAS} 115: E4594\textendash E4603 (2018).}

\cvitem{{[}20{]}}{\textbf{Meisburger SP}{*}, Thomas WC{*}, Watkins MB{*}, and Ando
N. \emph{X-ray scattering studies of protein structural dynamics}.
\textbf{Chem. Rev.} 117(12): 7615\textendash 72 (2017). {*}equal contribution}

\cvitem{{[}19{]}}{\textbf{Meisburger SP} \& Ando N. \emph{Correlated motions from
crystallography beyond diffraction.} \textbf{Acc. Chem. Res }50: 580\textendash 583
(2017).}

\cvitem{{[}18{]}}{Plumridge A, \textbf{Meisburger SP}, Andresen K, and Pollack L.
\emph{The impact of base stacking on the conformations and electrostatics
of single-stranded DNA.} \textbf{Nucl. Acids Res.} 45: 3932-3943 (2017).}

\cvitem{{[}17{]}}{Plumridge A{*}, \textbf{Meisburger SP}{*}, Pollack L. \emph{Visualizing
single-stranded nucleic acids in solution.} \textbf{Nucl. Acids Res.} 45(9): e66 (2017). {*}equal contribution}

\cvitem{{[}16{]}}{\textbf{Meisburger SP, }Taylor AB, Khan CA, Zhang S, Fitzpatrick
PF, Ando N. \emph{Domain movements upon activation of phenylalanine
hydroxylase characterized by crystallography and chromatography-coupled
small-angle X-ray scattering.} \textbf{JACS }138(20): 6506\textendash 16
(2016). }

\cvitem{{[}15{]}}{Chen Y, Tokuda JM, Topping T, \textbf{Meisburger SP}, Pabit SA,
Gloss LM, Pollack L. \emph{Asymmetric unwrapping of nucleosomal DNA
propagates asymmetric opening and dissociation of the histone core.}
\textbf{PNAS} 114: 334-339 (2016).}

\cvitem{{[}14{]}}{Rustiguel JK, Soares ROS, \textbf{Meisburger SP}, Davis KM, Malzbender
KL, Ando N, Dias-Baruffi M, Nonato MC. \emph{Full-length model of
the human galectin-4 and insights into dynamics of inter-domain communication.}
\textbf{Sci. Rep. }6: 33633 (2016). }

\cvitem{{[}13{]}}{\textbf{Meisburger SP}, Pabit SA, Pollack L. \emph{Determining the
locations of ions and water around DNA from X-ray scattering measurements.}
\textbf{Biophys. J.} 108: 2886-95 (2015).}

\cvitem{{[}12{]}}{Hopkins JB, Katz AM, \textbf{Meisburger SP}, Warkentin MA, Thorne
RE, Pollack L. \emph{A microfabricated fixed path length silicon sample
holder enables robust background subtraction for cryoSAXS}. \textbf{J.
Appl. Cryst.} 48: 227-37 (2015).}

\cvitem{{[}11{]}}{Chen Y, Tokuda JM, Topping T, Sutton JL, \textbf{Meisburger SP},
Pabit SA, Gloss LM, Pollack L. \emph{Revealing transient structures
of nucleosomes as DNA unwinds}. \textbf{Nucl. Acids Res.} 42: 8767-76
(2014).}

\cvitem{{[}10{]}}{Nguyen HT, Pabit SA, \textbf{Meisburger SP}, Pollack L, Case DA.
\emph{Accurate small and wide angle X-ray scattering profiles from
atomic models of proteins and nucleic acids}. \textbf{J. Chem. Phys.}
141: 22D508 (2014).}

\cvitem{{[}9{]}}{\textbf{Meisburger SP}, Sutton JL, Chen H, Pabit SA, Kirmizialtin
S, Elber R, Pollack L. \emph{Polyelectrolyte properties of single
stranded DNA measured using SAXS and single-molecule FRET: beyond
the wormlike chain model.} \textbf{Biopolymers} 99: 1032-45 (2013).}

\cvitem{{[}8{]}}{\textbf{Meisburger SP}, Warkentin M, Chen H, Hopkins JB, Gillilan
RE, Pollack L, Thorne RE. \emph{Breaking the radiation damage limit
with Cryo-SAXS.} \textbf{Biophys. J. }104(1): 227-36 (2013).}

\cvitem{{[}7{]}}{Chen H{*}, \textbf{Meisburger SP}{*}, Pabit SA, Sutton JL, Webb
WW, Pollack L. \emph{Ionic strength-dependent persistence lengths
of single-stranded RNA and DNA. }\textbf{PNAS} 109(3): 799-804 (2012). {*}equal contribution}

\cvitem{{[}6{]}}{Yoo TY{*}, \textbf{Meisburger SP}{*}, Hinshaw J{*}, Pollack L, Haran
G, Sosnick TR, Plaxco K. \emph{Small-angle X-ray scattering and single-molecule
FRET spectroscopy produce highly divergent views of the low-denaturant
unfolded state. }\textbf{J. Mol. Biol.} 418(3-4): 226-36 (2012). {*}equal contribution}

\cvitem{{[}5{]}}{Kirmizialtin S, Pabit SA, \textbf{Meisburger SP}, Pollack L, Elber
R. \emph{RNA and its ionic cloud: solution scattering experiments
and atomically detailed simulations.} \textbf{Biophys. J. }102(4):
819-28 (2012).}

\cvitem{{[}4{]}}{Blose JM, Pabit SA, \textbf{Meisburger SP}, Li L, Jones CD, Pollack
L. \emph{Effects of a protecting osmolyte on the ion atmosphere surrounding
DNA duplexes. }\textbf{Biochemistry} 50(40): 8540-7 (2011).}

\cvitem{{[}3{]}}{Li L, Pabit SA, \textbf{Meisburger SP}, Pollack L. \emph{Double-stranded
RNA resists condensation.} \textbf{Phys. Rev. Lett. }106: 108101 (2011).}

\cvitem{{[}2{]}}{Pabit SA, \textbf{Meisburger SP}, Li L, Blose JM, Jones CD, Pollack
L. \emph{Counting ions around DNA with anomalous small-angle X-ray
scattering.} \textbf{JACS }132(46): 16334-6 (2010).}

\cvitem{{[}1{]}}{Pabit SA, Qiu X, Lamb JS, Li L, \textbf{Meisburger SP}, Pollack
L. \emph{Both helix topology and counterion distribution contribute
to the more effective charge screening in dsRNA compared with dsDNA.}
\textbf{Nucl. Acids Res.} 37: 3887-96 (2009).}

\section{Patents}

\cvitem{{[}1{]}}{\textbf{Meisburger SP}, Warkentin MA, Hopkins JB, Katz AM, Pollack
L, and Thorne RE. (2018).\emph{ Apparatus and methods for low temperature
small angle X-ray scattering.} US 9,927,336 (June 4, 2012).}

\section{Presentations: Talks}

\cvitem{{[}15{]}}{U. at Buffalo, Protein Science Group Seminar. (Remote) Oct. 6, 2021. (Invited)}

\cvitem{{[}14{]}}{SSRL/LCLS Users' meeting. (Remote) Sep. 21, 2021. (Invited)}

\cvitem{{[}13{]}}{Harvard-Hamburg Crystallographic Curiosities Seminar Series. (Remote) May 27, 2021. (Invited)}

\cvitem{{[}12{]}}{SBGrid Weekly Webinar Series. (Remote) April 6, 2021. (Invited)}

\cvitem{{[}11{]}}{ACA Annual Meeting, Session 2.1.4: Frontiers in SAS. (Remote) Aug. 3, 2020. (Invited)}

\cvitem{{[}10{]}}{CHESS Commons Meeting. (Remote) Mar. 20, 2020. (Invited)}

\cvitem{{[}9{]}}{ACS Northeast Regional Meeting. Saratoga Springs, NY. June 25, 2019. (Invited)}

\cvitem{{[}8{]}}{Center for Nonlinear Studies, Los Alamos National Laboratory. Oct. 16, 2018. (Invited)}

\cvitem{{[}7{]}}{ACA Annual Meeting, Session 1.1.1: Closing the R-Factor Gap in Protein Crystallography. Toronto, Ontario. July 21, 2018. (Contributed)}

\cvitem{{[}6{]}}{ACA Annual Meeting, Session 1.1.1: Hybrid Methods - BioSAXS. New Orleans, LA. May 27, 2017. (Contributed)}

\cvitem{{[}5{]}}{ASBMB Annual Meeting, Spotlight Session: Structural Dynamics of Enzymes. Chicago, IL. April 24, 2017. (Contributed)}

\cvitem{{[}4{]}}{CHESS-U Workshop: Biomolecules in Motion. Ithaca, NY. June 8, 2016. (Invited)}

\cvitem{{[}3{]}}{Biophysical Society Meeting, Platform: DNA Structure and Dynamics. San Francisco, CA. Feb. 18, 2014. (Contributed)}

\cvitem{{[}2{]}}{CHESS Users\textquoteright{} Meeting. Ithaca, NY. June 2013. (Invited)}

\cvitem{{[}1{]}}{RNA-UNY. Rensselaerville, NY. Oct. 9, 2010. (Contributed)}

\section{Presentations: Posters (Selected)}

\cvitem{{[}6{]}}{Meisburger SP, Taylor AB, Khan CA, Zhang S, Fitzpatrick PF, Ando N. \emph{Unmixing Enzyme Allostery.}{*} CHESS Users' Meeting. June 2017. {*}\emph{Best poster: technical achievement}}

\cvitem{{[}5{]}}{Meisburger SP, Warkentin M, Chen
H, Hopkins JB, Katz AM, Gillilan RE, Thorne RE, Pollack L. \emph{Introducing Cryo-SAXS for measuring low resolution macromolecular structure without radiation damage.} Biophysical Society Meeting. Feb. 2013.}

\cvitem{{[}4{]}}{Meisburger SP, Gillilan RE, Woll A, Pollack L. \emph{A semi-transparent beamstop for accurate normalization of millisecond time-resolved SAXS profiles.} Chess Users' Meeting. June 2012.}

\cvitem{{[}3{]}}{Meisburger SP, Chen H, Pabit SA, Sutton JL, Webb WW, Pollack L. \emph{Solution structures of flexible RNA molecules in mono- and divalent salt.} Biophysical Society Meeting. Feb 2012.}

\cvitem{{[}2{]}}{Meisburger SP, Pabit SA, Li L, Blose JM, Brooks K, Hampel K, Pollack L. \emph{Measuring the dimensions of a compact kinetic intermediate in the folding pathway of the GlmS Ribozyme.} Biophysical Society Meeting. Feb 2011.}

\cvitem{{[}1{]}}{Meisburger SP, Pabit SA, Li L, Blose JM, Hampel K, Pollack L. \emph{Visualizing the structure of the glmS riboswitch as it folds using time-resolved SAXS.} Biophysical Society Meeting. Feb 2010.}

\section{Professional Memberships}

\cvitem{2020--}{American Association for the Advancement of Science (AAAS)}
\cvitem{2017--}{American Crystallographic Association (ACA)}
\cvitem{2009-2015}{Biophysical Society}

\section{Professional Activities}

\cvitem{Aug. 2021}{Session chair, ACA Meeting, \emph{BioWAXS: Experiment and Interpretation.}}
\cvitem{2021}{Chair, Small Angle Scattering Scientific Interest Group (SAS SIG) of the ACA}
\cvitem{Aug. 2020}{Session chair, ACA Meeting, \emph{Structural Dynamics I: Protein collective motions studied by X-ray scattering and diffraction.}}
\cvitem{2020}{Chair-elect, SAS SIG of the ACA}
\cvitem{Aug. 2019}{Session chair, ACA Meeting, \emph{Diffuse scattering for biological structure and dynamics.}}
\cvitem{2016-2019}{Elected member, CHESS User Executive Committee}
\cvitem{Feb. 2014}{Platform session chair, Biophysical Society Meeting}

\cvitem{2021--}{Reviewer for \emph{Structural Dynamics Journal}}
\cvitem{2020--}{Reviewer for \emph{Review of Scientific Instruments}}
\cvitem{2017--}{Reviewer for \emph{IUCrJ}}
\cvitem{2015--}{Reviewer for \emph{JACS}}


%\section{Mentoring \& Outreach}

\section{References}

\cvitem{}{Available upon request.}

%\renewcommand{\listitemsymbol}{} % Changes the symbol used for lists
%\cvlistdoubleitem{Nozomi Ando}{David Case}

\end{document}
